%-------------------------
% Resume in Latex
% Author : Jake Gutierrez (altered slightly by me)
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Kamila Kinel} \\ \vspace{1pt}
    \vspace{5pt}
    \small \raisebox{-0.1\height}\faPhone\ 702-767-9298 ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{kinelk1@unlv.nevada.edu}} ~ 
    \href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/kamila-kinel}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/KamilaKinel}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Nevada, Las Vegas}{Expected Graduation: Fall 2024}
      {Bachelor of Science in Computer Science}{}
  \resumeSubHeadingListEnd
      \vspace{0.5pt}
      \emph{Bachelor of Science in Mathematics}
%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Data Structures} $|$ \emph{C++}}{}
          \resumeItemListStart
            \resumeItem{Developed algorithms which utilized stacks, queues, linked lists, heaps, hash tables, hash graphs, and binary trees.}
            \resumeItem{Learned the fundamentals of time complexity and Big-O notation through practical application in coding projects.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Data Analysis and Visualization} $|$ \emph{Jupyter Notebook, Python} }{}
          \resumeItemListStart
            \resumeItem{Learned different methods of data analysis including traditional statistical methods, as well as contemporary machine learning and artificial intelligence techniques.}
            \resumeItem{Developed essential skills for dealing with large data sets.}
            \resumeItem{Gained familiarity with tools and libraries for performing data analysis in Python.}
            \resumeItem{Practiced organizing and presenting data for sharing and collaboration.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Linear Algebra}}{}
          \resumeItemListStart
            \resumeItem{Evaluated and used determinants to find the inverse of a matrix and to solve linear system.}
            \resumeItem{Learned the conditions under which a linear system has no solution, infinitely many solution, or unique solutions.}
            \resumeItem{Developed MATLAB code to solve a variety of linear algebra problems, including matrix operations and systems of linear equations.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}
%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
          \resumeProjectHeading
          {\textbf{Gaming Weapon Inventory Simulator} $|$ \emph{C++}}{}
          \resumeItemListStart
            \resumeItem{Employed object-oriented programming techniques to simulate the back-end of a weapon inventory system for games, similar to Fortnite.}
            \resumeItem{Utilized inheritance to create a hierarchy of inventory items, enhancing code modularity and reusability.}
            \resumeItem{Employed pointers and dynamic memory allocation for efficient memory management.}
              \vspace{-13pt}
          \resumeItemListEnd 
      \resumeProjectHeading
          {\textbf{Website: Macro Calculator} $|$ \emph{HTML/CSS, Java}}{}
          \resumeItemListStart
            \resumeItem{Currently working closely with a team member to design, develop, and launch a website dedicated to fitness and nutrition. }
            \resumeItem{Utilized technologies such as HTML, CSS, JavaScript, to design and develop the website's user interface and functionality.}
            \resumeItem{Continuously working on a dynamic macro nutrient calculator that will help users meet their fitness goals as well as track daily nutritional intakes.}
            \resumeItem{Participating in regular code reviews and discussions with the project partner to refine and enhance the project.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {C++ Tutor}{Fall 2022 -- Present}
      {Freelance}{Remote}
      \resumeItemListStart
        \resumeItem{Met with students one on one and explained core concepts such as pointers, structures, classes, ect.}
        \resumeItem{Helped with debugging code and improving algorithm efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {Nanny}{August 2019 --Present}
      {Private Families}{Las Vegas, Nevada}
      \resumeItemListStart
        \resumeItem{Provided part-time care to children ranging in age from infants to 8 years old.}
        \resumeItem{Designed educational activities based on play-based learning research, encompassing concepts like basic circuit board design, a variety of science experiments, and hands-on building projects.}
        \resumeItem{Assisted children with homework and school projects.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, MIPS, X86, HTML/CSS, Python, R, MATLAB} \\
     \textbf{Developer Tools}{: VS Code, Jupyter Notebook, Git} \\
    }}
 \end{itemize}
 \vspace{-16pt}


\end{document}
